---
title: "MAR Missing Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simulation results

Simulations are performed with Willd-bootstrap and 2000 permutation replicas. 
We analyze the number of rejects with a significance level of 5 percent. 
In the Wild boostrap the parameter $ln$ is selected as $ln=\sqrt(n)$, where $n$ is the number of data.

In this case, we suppose that $\mathbb{P}(\delta=1 | Z=(Z1,Z2)) = (1 + e^{-1+Z1+Z2})^{-1}$, where $Z_1 = Z_2 \sim \mathcal{N}(0,1)$ are two independent random variables. We fixed $n=300$.


```{r warning = FALSE, message=FALSE}
  source('simular_escenario_2.R')

  ns = 1 # Number of simulations
  n = 300
  p = 2
  rho = 0.2
  a1 = 0.30
  b1 = 0.05
  caso1 = 1
  caso2 = 1
  permutaciones = 10
  
  prs = c()
  for (i in 1:ns) {
    objeto = calcular_pvalor_escenario_2(n, p, a1, b1, rho, caso1, caso2)
    prs = c(prs, objeto$pv_rbf)
  }

  df = data.frame()
  df = rbind(df, c(a1, b1, rho, caso1, caso2, mean(prs <= 0.05)))
  
  print(prs)
  names(df) <- c("a1", "a2", "rho", "case1", "case2", "mean(prs $<$= 0.05)")

```

```{r message=TRUE}
  print(df)
```


